\documentclass[10pt]{article}
\usepackage[margin=3cm]{geometry}
\usepackage{amssymb}
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{capt-of}
\title{\bfseries\Huge Bram van den Akker}

\date{}
\begin{document}
\title{MPI}
\author{Abe Wiersma, Bram van den Akker}
\date{\today}
\maketitle
\newpage

\section{Openmp vs pthreads vs MPI}
Because MPI's implementation of multi-processing is so different from the Openmp's and phtreads' implementation a thurough rewrite of the framework is needed:
All IO is done from process 0, \'the master process\', after the IO is done, the work is divided over the master and worker threads.
This is done by MPI\_send's and MPI\_recv's, after this every process starts the simulation with their respected parts of the data.
In the simulation each process receives data from their left and right neighbor.
After the simulation is done after t\_steps, the result is sent to the master process, where a non-blocking IRecv receives data into results. The master process waits until all results are received with a wait\_all.

Despite the hard work we put in we did not bare the fruits of our labours, segfaults kept us from running on the das4,
and on our local machines these same segfaults kept us from using more than 5 processes per node.
We think the problem lies in mpi breaking the alloc's, and data being overwritten, but because in MPI it is hard to diagnose problems we just cannot be sure.

\section{3.2 Collective communication}
The collective communication assignment was fairly simple. We created three different broadcast methods. 

\subsection{Simple broadcast}
The simple broadcast has one root not which will send it's message to all the other nodes in the network. This is achieved the use of MPI\_Send and MPI\_Recv.
\subsection{One way circle broadcast}
To create a real peer to peer broadcast we used a circle broadcast. The root will send the message to it´s right neighbour, each neighbour will send the message to it´s right neighbour until the root is reached again. 
\subsection{Two way circle broadcast}
Improving the circle broadcast performance can be achieved by sending the message in two directions. The root will send the message to it´s left and right neighbours. When a node receives the message from one neighbour it will send the message to the neighbour on the other side. Mssages will only travel through one half of the circle. For an even amount of messages the messages per circle half can be calculated by $(world size / 2) - 1$, for uneven messages the right half will do send $(world size / 2)$ amount of messages.


\end{document}